On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-08 manuscripts/IEEE/final_submission.tex
chaz edits

The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $A$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.  Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is essentially linear in desired accuracy $\delta_1, \delta_2$.

In the next section, we give precise statements of these findings.  We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the number of nonzero entries in sparse codes.

@@

Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness stability even when generating $A$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $B$ have more columns than $A$.  Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest. We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}). We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix). Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions. 
%The Appendix contains a proof of Lem.~\ref{MainLemma}.

@@

We generalize the matrix lower bound for our purposes by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices. Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).  In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.  We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
%\begin{align*} 
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
%\end{align*} 
%
%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$. Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$. For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
%\end{align*} 
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
%\end{align*} 
\begin{align}\label{Ldef}
L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
\end{align} 
%
writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}

As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}. Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.  Finally, we say that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.
Note that sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$).

@@

\begin{theorem}\label{DeterministicUniquenessTheorem}
Fix integers $n, k, m$ and $\overline m$. Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}. If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:

@@

%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: 
In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively.

In the important special case when $\overline m = m$, the theorem directly implies (e.g., Fig.~\ref{noisyrecovery}) that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$: 
\begin{align}\label{epsdel}
\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
\end{align}

\begin{corollary}\label{DeterministicUniquenessCorollary}
Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with $L_{2k}(\mathbf{A}) > 0$ generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
\end{corollary}

@@

To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has $\nu_{\ell}$ absolutely continuous with respect to $\mu$ for all $\ell \in [p]$, where $\mu$ is the standard Borel measure on $\mathbb{R}$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).  This fact combined with Thm.~\ref{robustPolythm} implies the following.

\begin{corollary}\label{ProbabilisticCor}
If indeterminate entries of $\mathbf{A}$ and $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
\end{corollary}

@@

We close with some remaining open questions.  First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniquness and stability in sparse coding.  Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?

>>>>

The main result of this work is a very general uniqueness theorem for sparse coding (Thm.~\ref{DeterministicUniquenessTheorem}) directly 
implying (Cor.~\ref{DeterministicUniquenessCorollary}) that stable representations of a dataset $Z$ are guaranteed whenever generating dictionaries $\mathbf{A}$ satisfy a spark condition on supports and the original sparse codes $\mathbf{x}_i$ are sufficiently diverse.  Moreover, we provide an explicit, computable $\varepsilon(\delta_1, \delta_2)$ in (\ref{epsdel}) that is essentially linear in desired accuracy $\delta_1, \delta_2$.

In the next section, we give precise statements of these findings.  We then extend the same guarantees (Thm.~\ref{SLCopt}) to the following alternate formulation of dictionary learning, which minimizes the total number of nonzero entries in sparse codes.

@@

Our development of Thm.~\ref{DeterministicUniquenessTheorem} is general enough to provide some uniqueness and stability even when generating $\mathbf{A}$ do not fully satisfy (\ref{SparkCondition}) and recovery dictionaries $\mathbf{B}$ have more columns than $\mathbf{A}$.  Moreover, the approach incorporates a combinatorial theory for designing generating codes that should be of independent interest. We also give brief arguments adapting our results to dictionaries and codes drawn from probability distributions (Cor.~\ref{ProbabilisticCor}). We defer to Sec.~\ref{DUT} the technical proofs of Thms.~\ref{DeterministicUniquenessTheorem} and ~\ref{SLCopt}, following some necessary definitions and a useful fact in combinatorial matrix analysis (Lem.~\ref{MainLemma}; proved in the Appendix). Finally, we discuss in Sec.~\ref{Discussion} applications of our mathematical observations as well as open questions. 
%The Appendix contains a proof of Lem.~\ref{MainLemma}.

@@

We generalize the matrix lower bound for our purposes by restricting it to the spans of certain submatrices\footnote{See \cite{vidal2005generalized} for an overview of the related ``union of subspaces" model.} associated with a hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ of column indices. Let $\mathbf{M}_S$ denote the submatrix formed by the columns of a matrix $\mathbf{M}$ indexed by $S \subseteq [m]$ (setting $\mathbf{M}_\emptyset := \mathbf{0}$).  In the sections that follow, we shall also let $\bm{\mathcal{M}}_S$ denote the column-span of a submatrix $\mathbf{M}_S$, and $\bm{\mathcal{M}}_\mathcal{G}$ to denote $\{\bm{\mathcal{M}}_S\}_{S \in \mathcal{G}}$.  We define:  % Define $L_\mathcal{H}(\mathbf{M})$ as follows:
%\begin{align*} 
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}(\mathbf{x}_1-\mathbf{x}_2)\|_2 }{ \sqrt{2k} \|\mathbf{x}_1-\mathbf{x}_2\|_2} : \mathbf{x}_1, \mathbf{x}_2 \in \cup_{S \in \mathcal{H}} \bm{\mathcal{M}}_S \right\},
%\end{align*} 
%
%where we write $L_{2k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$. Note that if $\mathcal{H}$ covers $[m]$, then $L_2 > L_\mathcal{H}$.\footnote{The reader should beware that $L_2 = L_{[m]}$, whereas $L = L_{\{[m]\}}$. For even $k$, the quantity $1 - \sqrt{k} L_k(\mathbf{M})$ is also known in the compressed sensing literature as the (asymmetric) lower restricted isometry constant \cite{Blanchard2011}.} Clearly, for any $\mathbf{M}$ satisfying \eqref{SparkCondition}, we have $L_{k'}(\mathbf{M}) > 0$ for  $k' \leq 2k$.
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{ \|\mathbf{M}_S\mathbf{x}\|_2 }{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H} \right\},
%\end{align*} 
%\begin{align*}
%L_\mathcal{H}(\mathbf{M}) := \max \left\{ \ falpha: \|\mathbf{M}_S\mathbf{x}\|_2 \geq \alpha \sqrt{k} \|\mathbf{x}\|_2 : S \in \mathcal{H}, \ \ \mathbf{x} \in \mathbb{R}^m \right\},
%\end{align*} 
\begin{align}\label{Ldef}
L_\mathcal{H}(\mathbf{M}) := \min \left\{ \frac{\|\mathbf{M}_S\mathbf{x}\|_2}{ \sqrt{k} \|\mathbf{x}\|_2} : S \in \mathcal{H}, \ \mathbf{0} \neq \mathbf{x} \in \mathbb{R}^{|S|} \right\},
\end{align} 
%
writing also $L_{k}$ in place of $L_\mathcal{H}$ when $\mathcal{H} = {[m] \choose k}$.\footnote{In compressed sensing literature, \mbox{$1 - \sqrt{k} L_k(\mathbf{M})$}  is the asymmetric lower restricted isometry constant for $\mathbf{M}$ with unit $\ell_2$-norm columns \cite{Blanchard2011}.}  As explained above, compactness implies that $L_{2k}(\mathbf{M}) > 0$ for all $\mathbf{M}$ satisfying \eqref{SparkCondition}. Clearly, $L_{\mathcal{H}'}(\mathbf{M}) \geq L_\mathcal{H}(\mathbf{M})$ whenever $\mathcal{H}' \subseteq \mathcal{H}$, and any $k$-uniform $\mathcal{H}$ satisfying $\cup \mathcal{H} = [m]$ has $L_2 \geq L_{2\mathcal{H}} \geq L_{2k}$.

@@

\begin{theorem}\label{DeterministicUniquenessTheorem}
Fix integers $n, k, m$ and $\overline m$. Suppose that the $n \times m$ matrix $\mathbf{A}$ satisfies $L_{2\mathcal{H}}(\mathbf{A}) > 0$ for some $r$-regular $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP from Def.~\ref{sip}. If $k$-sparse \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N$} include more than $(k-1){\overline m \choose k}$ vectors in general linear position\footnote{Recall that a set of vectors sharing support $S$ are in \emph{general linear position} when any $|S|$ of them are linearly independent.} supported in each $S \in \mathcal{H}$, then there is $C_1 > 0$ for which the following holds for all%\footnote{The condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise,  with \mbox{$\mathbf{A}$ = $\mathbf{I}$} and $\mathbf{x}_i = \mathbf{e}_i$, there is a matrix $\mathbf{B}$ and $1$-sparse $\mathbf{\overline{x}}_i$ with $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ that nonetheless violates \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:
\footnote{Note that the condition $\varepsilon < L_2(\mathbf{A}) /C_1$ is necessary; otherwise, with \mbox{$\mathbf{A}$ = $\mathbf{I}$} (the identity matrix) and $\mathbf{x}_i = \mathbf{e}_i$, the matrix $\mathbf{B} = \left[\mathbf{0}, \frac{1}{2}(\mathbf{e}_1 + \mathbf{e}_2), \mathbf{e}_3, \ldots, \mathbf{e}_{m} \right]$ and sparse codes $\mathbf{\overline x}_i = \mathbf{e}_2$ for $i = 1, 2$ and $\mathbf{\overline x}_i = \mathbf{e}_i$ for $i \geq 3$ satisfy $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline{x}}_i \|_2 \leq \varepsilon$ but nonetheless violate \eqref{Cstable}.} $\varepsilon < L_{2}(\mathbf{A}) / C_1$:

@@

%We delay defining the explicit constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).
%To be clear, the implication of Thm.~\ref{DeterministicUniquenessTheorem} is that $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with \eqref{def1} guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: 
In words, Thm.~\ref{DeterministicUniquenessTheorem} says that the smaller the regularity $r$ of original support hypergraph $\mathcal{H}$ or the difference $\overline m - m$ between assumed and actual number of elements in the latent dictionary, the more columns and coefficients of the original dictionary $\mathbf{A}$ and sparse codes $\mathbf{x}_i$ are guaranteed to be contained (up to noise) in the appropriately labelled and scaled recovered dictionary $\mathbf{B}$ and codes $\mathbf{\overline x}_i$, respectively. 
In the important special case when $\overline m = m$, the theorem directly implies (e.g., Fig.~\ref{noisyrecovery}) that  $Y = \{\mathbf{Ax}_1, \ldots, \mathbf{Ax}_N\}$ has a stable $k$-sparse representation in $\mathbb{R}^m$, with inequalities \eqref{def1} guaranteed in Def.~\ref{maindef} for the following worst-case error $\varepsilon$: 
\begin{align}\label{epsdel}
\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \delta_2 + \max_{i \in [N]} \|\mathbf{x}_i\|_1  \right) } \right\}.
\end{align}

Note that sparse codes in general linear position are straightforward to produce deterministically with a ``Vandermonde''  construction (i.e., by choosing columns of the matrix $[\gamma_{i}^j]_{i,j=1}^{k,N}$, for distinct nonzero $\gamma_i$). We therefore have the following direct consequence of Thm.~\ref{DeterministicUniquenessTheorem}.

\begin{corollary}\label{DeterministicUniquenessCorollary}
Given any regular hypergraph $\mathcal{H} \subseteq {[m] \choose k}$ with the SIP, there are $N =  |\mathcal{H}| \left[ (k-1){m \choose k} + 1  \right]$ vectors \mbox{$\mathbf{x}_1, \ldots, \mathbf{x}_N \in \mathbb{R}^m$} such that every matrix $\mathbf{A}$ with satisfying \eqref{SparkCondition} generates a dataset $Y = \{\mathbf{A}\mathbf{x}_1, \ldots, \mathbf{A}\mathbf{x}_N\}$ with a stable $k$-sparse representation in $\mathbb{R}^m$ for $\varepsilon(\delta_1,\delta_2)$ given by \eqref{epsdel}.
\end{corollary}

@@

To extend this observation to arbitrary probability distributions, note that if a set of measure spaces $\{(X_{\ell}, \nu_{\ell})\}_{\ell=1}^p$ has measures $\nu_{\ell}$ absolutely continuous with respect to the standard Borel measure on $\mathbb{R}$ for all $\ell \in [p]$, then the product measure $\prod_{\ell=1}^p \nu_{\ell}$ is also absolutely continuous with respect to the standard Borel product measure on $\mathbb{R}^p$ (e.g., see \cite{folland2013real}).  This fact combined with Thm.~\ref{robustPolythm} implies the following.

\begin{corollary}\label{ProbabilisticCor}
If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability measures absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
\end{corollary}

@@

We close with some remaining open questions.  First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.  Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}? In what special cases is it efficient to check that a solution to the problems is optimal?
